E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-14 Background/history.tex
fixed citation spaces

E-Mail Header Injection seems to have been first documented over a decade ago, in a late 2004 article on phpsecure.info \cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the \texttt{mail()} function in PHP, and how it can be exploited. More recently, a blog post by Damon Kohler \cite{DK} and an accompanying wiki article \cite{Injection} describe the attack vector and outline a few defense measures for the same.

>>>>

E-Mail Header Injection seems to have been first documented over a decade ago, in a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the \texttt{mail()} function in PHP, and how it can be exploited. More recently, a blog post by Damon Kohler~\cite{DK} and an accompanying wiki article~\cite{Injection} describe the attack vector and outline a few defense measures for the same.

### 2016-05-14 Background/impact.tex
condensing pocs
fixed citation spaces

The impact of the vulnerability can be pretty far-reaching.
Table~\ref{tab:usage} shows the current server-side language usage statistics on the Web \cite{W3techs}.

\begin{table}[!tb]
	\centering
	\begin{tabular}{|p{4cm}|p{4cm}|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Server Side Language}} & \multicolumn{1}{c|}{\textbf{\% of Usage}}\\
		\hline
		PHP & 81.9\\
		\hline    
		ASP.NET & 15.8\\
		\hline
		Java & 3.1\\
		\hline
		Ruby & 0.6\\
		\hline
		Perl & 0.5\\
		\hline
		JavaScript & 0.2\\
		\hline
		Python & 0.2\\
		\hline

	\end{tabular}
	\caption[\titlecap{Language usage statistics}]{Language usage statistics compiled from w3techs \cite{W3techs}.}
	\label{tab:usage}
\end{table}

@@

\begin{itemize}
	\item Phishing and Spoofing Attacks\\
    Phishing \cite{wiki:Phishing} (a variation of spoofing \cite{wiki:Spoofing_attack}) refers to an attack where the recipient of an e-mail is made to believe that the e-mail is a legitimate one. The e-mail usually redirects them to a malicious website, which then steals their credentials.

>>>>

The impact of the vulnerability can be pretty far-reaching.
Table~\ref{tab:usage} shows the current server-side language usage statistics on the Web~\cite{W3techs}.

\begin{table}[!tb]
	\centering
	\begin{tabular}{|p{4cm}|p{4cm}|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Server Side Language}} & \multicolumn{1}{c|}{\textbf{\% of Usage}}\\
		\hline
		PHP & 81.9\\
		\hline
		Java & 3.1\\
		\hline
		Ruby & 0.6\\
		\hline
		Python & 0.2\\
		\hline

	\end{tabular}
	\caption[\titlecap{Language usage statistics}]{Language usage statistics compiled from w3techs~\cite{W3techs}.}
	\label{tab:usage}
\end{table}

@@

\begin{itemize}
	\item Phishing and Spoofing Attacks\\
    Phishing~\cite{wiki:Phishing} (a variation of spoofing~\cite{wiki:Spoofing_attack}) refers to an attack where the recipient of an e-mail is made to believe that the e-mail is a legitimate one. The e-mail usually redirects them to a malicious website, which then steals their credentials.

### 2016-05-14 Background/lang_aff.tex
fixed citation spaces

\begin{itemize}
\item{\textbf{PHP}} - PHP was one of the first languages found to have this vulnerability in its implementation of the \texttt{mail()} function at the time of release of PHP~4.0. The early finding of this vulnerability can be attributed in part to the success and popularity of the language for creating web pages. According to w3techs \cite{W3techs}, PHP is used by 81.9\% of all the websites in existence, thereby creating the possibility of this vulnerability to be widespread.

After 13 further iterations of the language since the 4.0 release (the current version is 7.1), the \texttt{mail()} function is yet to be fixed after 15 years. However, it is specified in the PHP documentation \cite{PHPDocs} that the \texttt{mail()} function does not protect against this vulnerability.
A working code sample of the vulnerability, written in PHP~5.6 (latest well-supported version), is shown in  Listing~\ref{code:phpemi}.

@@

\item{\textbf{Java}} -
Java has a bug report about E-Mail Header Injection filed against its JavaMail API. A detailed write-up by Alexandre Herzog \cite{Herzog.2014} is complete with a proof of concept program that exploits the API to inject headers.

>>>>

\begin{itemize}
\item{\textbf{PHP}} - PHP was one of the first languages found to have this vulnerability in its implementation of the \texttt{mail()} function at the time of release of PHP~4.0. The early finding of this vulnerability can be attributed in part to the success and popularity of the language for creating web pages. According to w3techs~\cite{W3techs}, PHP is used by 81.9\% of all the websites in existence, thereby creating the possibility of this vulnerability to be widespread.

After 13 further iterations of the language since the 4.0 release (the current version is 7.1), the \texttt{mail()} function is yet to be fixed after 15 years. However, it is specified in the PHP documentation~\cite{PHPDocs} that the \texttt{mail()} function does not protect against this vulnerability.
A working code sample of the vulnerability, written in PHP~5.6 (latest well-supported version), is shown in  Listing~\ref{code:phpemi}.

@@

\item{\textbf{Java}} -
Java has a bug report about E-Mail Header Injection filed against its JavaMail API. A detailed write-up by Alexandre Herzog~\cite{Herzog.2014} is complete with a proof of concept program that exploits the API to inject headers.

### 2016-05-14 Background/pbm_bg.tex
slight formatting changes done
fixed most emph/quote/texttt issues
fixed citation spaces

\section{Problem Background}

E-Mail Header Injection belongs to a broad class of vulnerabilities known simply as injection attacks. However, unlike its more popular siblings, SQL injection \cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting (XSS) \cite{Injection1}, \cite{KleinAmit} or even HTTP Header Injection \cite{sessionride}, relatively little research is available on E-Mail Header Injection.

>>>>

E-Mail Header Injection belongs to a broad class of vulnerabilities known simply as injection attacks. However, unlike its more popular siblings, SQL injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting (XSS) \cite{Injection1}, \cite{KleinAmit} or even HTTP Header Injection~\cite{sessionride}, relatively little research is available on E-Mail Header Injection.

### 2016-05-14 Discussion/lessons.tex
fixed citation spaces

\subsection{Lessons Learned}
    From our results, it is evident that the vulnerability exists in the wild. Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we take the total number of websites on the World Wide Web --- 1,018,863,952 according to Internet Live Stats \cite{InternetLiveStats2016} as of early 2016 --- and calculate \successDelta\ percent (the occurrence rate of E-Mail Header Injection vulnerability as found by our system) of that number, we end up with 11,309,390 websites - a pretty significant number. We agree that an extrapolation of that kind might not be an accurate measure of the prevalence of the vulnerability. However, even with as few as a thousand websites affected by this vulnerability, it can still have a disastrous impact on these websites, and also on overall World Wide Web due to the traffic caused by the sheer number of generated e-mails.

>>>>

\subsection{Lessons Learned}
    From our results, it is evident that the vulnerability exists in the wild. Despite its relatively low occurrence rate compared to the more popular SQL Injection and XSS (Cross-Site Scripting), when we take the total number of websites on the World Wide Web --- 1,018,863,952 according to Internet Live Stats~\cite{InternetLiveStats2016} as of early 2016 --- and calculate \successDelta\ percent (the occurrence rate of E-Mail Header Injection vulnerability as found by our system) of that number, we end up with 11,309,390 websites - a pretty significant number. We agree that an extrapolation of that kind might not be an accurate measure of the prevalence of the vulnerability. However, even with as few as a thousand websites affected by this vulnerability, it can still have a disastrous impact on these websites, and also on overall World Wide Web due to the traffic caused by the sheer number of generated e-mails.

### 2016-05-14 Discussion/limits.tex
fixed citation spaces

\subsection[Limitations]{Limitations of the Project}
\label{limitations}
	This section complements Section \ref{sys:issues}, and discusses the limitations of our project. The following list, although not exhaustive, goes into the limitations of our project in detail: 
	\begin{itemize}
		\item CAPTCHAs - As noted in section \ref*{issues:captcha}, CAPTCHAs pose a significant problem to our automated system. As CAPTCHAs are designed to be robust, there is no easy way to break them. There has been considerable research in this area \cite{captchas2}, \cite{captchas} to name a few and although not impossible to break, it remains out of the scope of this project, and thus, we chose to ignore websites which require CAPTCHA verification.
		\item JavaScript Apps - Due to the growing emphasis on responsive web applications, more and more single-page web applications are being built purely with JavaScript. Even conventional applications are now making use of JavaScript to dynamically insert content and update the pages. This means that these dynamically injected components are not a part of the initial source code that is sent to the client by the web server.

>>>>

\subsection[Limitations]{Limitations of the Project}
\label{limitations}
	This section complements Section \ref{sys:issues}, and discusses the limitations of our project. The following list, although not exhaustive, goes into the limitations of our project in detail: 
	\begin{itemize}
		\item CAPTCHAs - As noted in section \ref*{issues:captcha}, CAPTCHAs pose a significant problem to our automated system. As CAPTCHAs are designed to be robust, there is no easy way to break them. There has been considerable research in this area~\cite{captchas2}, \cite{captchas} to name a few and although not impossible to break, it remains out of the scope of this project, and thus, we chose to ignore websites which require CAPTCHA verification.
		\item JavaScript Apps - Due to the growing emphasis on responsive web applications, more and more single-page web applications are being built purely with JavaScript. Even conventional applications are now making use of JavaScript to dynamically insert content and update the pages. This means that these dynamically injected components are not a part of the initial source code that is sent to the client by the web server.

### 2016-05-14 Discussion/mitigation.tex
chap6 added
chap7 added
fixed citation spaces

\section[Mitigation Strategy]{How to prevent this attack}
\label{disc:mitigation}
This section describes the most common measures that can be taken to prevent the occurrence of this vulnerability, or at least reduce the impact.
\begin{itemize}
	\item Use Mail Libraries\\
	This is the preferred way of combating this vulnerability. Using a library that is well tested can remove the burden of input sanitization from the developer. Also, since most of these libraries are open-source, bugs are identified quicker and fixes are readily available.
	A list of known secure libraries for each popular language and framework is shown in Table~\ref{tab:maillib}.

	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of E-Mail Header Injection vulnerability.
	\begin{table}[!htbp]
		\centering
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website: https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
			\hline
			Python & SMTPLib with email.header.Header\tablefootnote{instead of using email.parser.Parser to parse the header}\\
			\hline
			Java & Apache Commons E-Mail\tablefootnote{Apache Commons E-Mail: https://commons.apache.org/proper/commons-email/}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\tablefootnote{Ruby Mail Website: https://rubygems.org/gems/mail}\\
			\hline
			WordPress & Contact Form 7\tablefootnote{Contact Form 7 Download: https://wordpress.org/plugins/contact-form-7/}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
		\label{tab:maillib}
	\end{table}
	% changes to be made amrked in sublime
	\item Use a Content Management System (CMS) \\
	Content management systems like WordPress and Drupal include certain libraries and plugins to prevent E-Mail Header Injection. Thus, websites built with such CMS' are usually resistant to these attacks. However, it is advised to use the right E-Mail plugins when using such CMS', as not all plugins might be secure.
	An example of a secure plug-in is included as part of Table~\ref{tab:maillib}.

	\item Input Validation\\
	If neither of the two options above is feasible, due to reasons such as the website being an in-house production, or due to lack of support infrastructure, developers can choose to perform proper input sanitization. Sanitization should be done keeping in mind RFC5322 \cite{rfc5322}, and care must be taken to ensure that all edge cases are taken into account.

>>>>

\subsection[Mitigation Strategy]{How to prevent this attack}
\label{disc:mitigation}
This section describes the most common measures that can be taken to prevent the occurrence of this vulnerability, or at least reduce the impact.
\begin{itemize}
	\item Use Mail Libraries\\
	This is the preferred way of combating this vulnerability. Using a library that is well tested can remove the burden of input sanitization from the developer. Also, since most of these libraries are open-source, bugs are identified quicker and fixes are readily available.
	A list of known secure libraries for each popular language and framework is shown in Table~\ref{tab:maillib}.

	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of E-Mail Header Injection vulnerability.
	\begin{table}[!htbp]
		\centering
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website: https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
			\hline
			Python & SMTPLib with email.header.Header\tablefootnote{instead of using email.parser.Parser to parse the header}\\
			\hline
			Java & Apache Commons E-Mail\tablefootnote{Apache Commons E-Mail: https://commons.apache.org/proper/commons-email/}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\tablefootnote{Ruby Mail Website: https://rubygems.org/gems/mail}\\
			\hline
			WordPress & Contact Form 7\tablefootnote{Contact Form 7 Download: https://wordpress.org/plugins/contact-form-7/}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
		\label{tab:maillib}
	\end{table}
	\item Use a Content Management System (CMS) \\
	Content management systems like WordPress and Drupal include certain libraries and plugins to prevent E-Mail Header Injection. Thus, websites built with such CMS' are usually resistant to these attacks. However, it is advised to use the right E-Mail plugins when using such CMS', as not all plugins might be secure.
	An example of a secure plug-in is included as part of Table~\ref{tab:maillib}.

	\item Input Validation\\
	If neither of the two options above is feasible, due to reasons such as the website being an in-house production, or due to lack of support infrastructure, developers can choose to perform proper input sanitization. Sanitization should be done keeping in mind RFC5322~\cite{rfc5322}, and care must be taken to ensure that all edge cases are taken into account.

### 2016-05-14 System/components.tex
fixed citation spaces

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
The Fuzzer is the heart of the system and is the only component that interacts directly with the external websites. The Fuzzer is split into smaller modules, each of which is responsible for a particular type of fuzzing.  We inject payloads in two different stages, to improve the efficiency, and reduce the total number of HTTP requests we generate. This is because making HTTP requests is an expensive process \cite{McGrath2009}, and can be a cause of bottlenecks in a Crawler-Fuzzer system \cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads we use for fuzzing are:
\paragraph{Non-Malicious Payload}
\label{Comp:Fuzzer:nmp}
The regular or non-malicious payload is a straight forward E-Mail address of the format -- \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by our internal \texttt{form\_id}, to create a one-to-one mapping of the payloads to the forms, and \texttt{example.com} is replaced by the required domain.
This non-malicious payload allows us to check whether we can inject data into a form and whether we can overcome the `anti-bot' measures on the given website, without attempting to fuzz the website.

@@

\paragraph{Analyzing e-mail with payloads}
The `e-mails with payloads' refer to e-mails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts. These e-mails were received due to injecting the malicious payloads that were discussed in Section. \ref{Comp:Fuzzer:mp}. Analysis of these e-mails is considerably simpler than that of the regular e-mails. This is due to the fact that this involves lesser processing of the contents of the e-mail compared to the previous section.
\paragraph{Detecting injected bcc headers}
As discussed in the payloads section (\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field. Thus, we simply parse the E-Mails and store them in the Database.

\label{analyze:detect_x_check}
\paragraph{Detecting injected x-check headers}
E-Mails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of e-mails.
These e-mails could have been generated due to two reasons:
\begin{enumerate}
	\item The websites performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending e-mails only to the \texttt{nuser} account. These e-mails then act as proof that the vulnerability was not found on the given website.
	\item A more conducive scenario is when the \texttt{bcc} header was ignored for some reason, e.g.\ Python's default behavior when it encounters duplicate headers. In this case, we check whether the e-mail contains the custom header \texttt{x-check}. If it does, then this is a successful exploit of the vulnerability, and we store it in the database.
\end{enumerate}

>>>>

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
The Fuzzer is the heart of the system and is the only component that interacts directly with the external websites. The Fuzzer is split into smaller modules, each of which is responsible for a particular type of fuzzing.  We inject payloads in two different stages, to improve the efficiency, and reduce the total number of HTTP requests we generate. This is because making HTTP requests is an expensive process~\cite{McGrath2009}, and can be a cause of bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads we use for fuzzing are:
\paragraph{Non-Malicious Payload}
\label{Comp:Fuzzer:nmp}
The regular or non-malicious payload is a straight forward E-Mail address of the format -- \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by our internal \texttt{form\_id}, to create a one-to-one mapping of the payloads to the forms, and \texttt{example.com} is replaced by the required domain.
This non-malicious payload allows us to check whether we can inject data into a form and whether we can overcome the `anti-bot' measures on the given website, without attempting to fuzz the website.

@@

\paragraph{Analyzing e-mail with payloads}
The `e-mails with payloads' refer to e-mails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts. These e-mails were received due to injecting the malicious payloads that were discussed in Section. \ref{Comp:Fuzzer:mp}. Analysis of these e-mails is considerably simpler than that of the regular e-mails. This is due to the fact that this involves lesser processing of the contents of the e-mail compared to the previous section.
\paragraph{Detecting injected \texttt{bcc} headers}
As discussed in the payloads section (\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field. Thus, we simply parse the E-Mails and store them in the Database.

\label{analyze:detect_x_check}
\paragraph{Detecting injected \texttt{x-check} headers}
E-Mails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of e-mails.
These e-mails could have been generated due to two reasons:
\begin{enumerate}
	\item The websites performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending e-mails only to the \texttt{nuser} account. These e-mails then act as proof that the vulnerability was not found on the given website.
	\item A more conducive scenario is when the \texttt{bcc} header was ignored for some reason, e.g.\ Python's default behavior when it encounters duplicate headers. In this case, we check whether the e-mail contains the custom header \texttt{x-check}. If it does, then this is a successful exploit of the vulnerability, and we store it in the database.
\end{enumerate}

### 2016-05-14 System/issues.tex
fixed citation spaces

	\item Bot Blockers\\
	\label{issues:captcha}
    Because our system is fully automated, it is also susceptible to being stopped by `bot-blockers' i.e.\ mechanisms built-in to a website to prevent automated crawls or form submissions. Measures like CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots \cite{captchas3}, \cite{captchas2}.

>>>>

	\item Bot Blockers\\
	\label{issues:captcha}
    Because our system is fully automated, it is also susceptible to being stopped by `bot-blockers' i.e.\ mechanisms built-in to a website to prevent automated crawls or form submissions. Measures like CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots~\cite{captchas3}, \cite{captchas2}.

### 2016-05-14 System/proof_of_concept.tex
fixed citation spaces

\subsection{Proof of Concept Attacks}
The previous section (Section~\ref{Arch:Test}) discussed in detail how we verified that our system functions according to our expectations. This section describes how we validated our expectations. In order to do this, we constructed three sets of web applications in PHP, Python, and Ruby. Each of these applications was a simple web app that accepted user input to construct and send an E-Mail.

The front-end for each of the three applications is shown in Listing~\ref{code:html}. The server-side code for the three languages are shown in Listings~\ref{code:phpemi}, \ref{code:pyemi}, and \ref{code:rubyemi}.

@@

A similar injection example for PHP is shown in Figure~\ref{fig:postmanphp} and the corresponding e-mail caught by MailCatcher is shown in Figure~\ref{fig:mailcatcherphp}. The astute reader might have noticed that in the given examples we have used \texttt{\%0a} to separate the headers, while in Section~\ref{Comp:Fuzzer:mp}, we had used \texttt{\textbackslash{}n}. This is due to URL encoding \cite{rfc1738}, wherein special characters in th URL are `encoded' or `escaped' with their ASCII equivalent.
The reason why we do not have to do this with the payloads our system injects is due to the fact that the Python Requests library that we use to generate the HTTP requests automatically does this encoding for us.

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=14cm, height=8cm]{System/EMI_Postman_PHP}
	\caption[\titlecap{Fuzzing a request for the PHP backend}]{Fuzzing a request for the PHP backend, the payload can be seen inside the address bar on top.}
	\label{fig:postmanphp}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=14cm, height=8cm]{System/EMI_Mailcatcher_PHP}
	\caption[\titlecap{E-Mail header injection proof of concept - PHP}]{E-Mail header injection proof of concept - PHP, we can see that multiple headers (bcc, x-check, subject) have been inserted into the resulting e-mail.}
	\label{fig:mailcatcherphp}
\end{figure}

>>>>

\subsection*{Proof of Concept Attacks}
This section describes how we validated our expectations. In order to do this, we constructed three sets of web applications in PHP, Python, and Ruby. Each of these applications was a simple web app that accepted user input to construct and send an E-Mail.

The front-end for each of the three applications is shown in Listing~\ref{code:html}. The server-side code for the PHP and Python are shown in Listings~\ref{code:phpemi} and \ref{code:pyemi} respectively.

@@

The astute reader might have noticed that in the given example we have used \texttt{\%0a} to separate the headers, while in Section~\ref{Comp:Fuzzer:mp}, we had used \texttt{\textbackslash{}n}. This is due to URL encoding~\cite{rfc1738}, wherein special characters in th URL are `encoded' or `escaped' with their ASCII equivalent.
The reason why we do not have to do this with the payloads our system injects is due to the fact that the Python Requests library that we use to generate the HTTP requests automatically does this encoding for us.

@@

### 2016-05-14 exp_setup.tex
fixed citation spaces

\section{Evaluation}
This chapter describes the experimental setup for our project including the servers used, the software and the platforms involved, the languages used, and the task queue system that was used for parallelism. We follow this up with our evaluation of the system, with a test suite, and proof of concept examples.

\input{Experiment/sys_config}
\input{Experiment/platform}
\input{Experiment/languages}
\input{Experiment/celery}
\input{System/test_plan}
\input{System/proof_of_concept}

>>>>

\section{Implementation}

\input{Experiment/sys_config}
%\input{Experiment/platform}
%\input{Experiment/languages}
%\input{Experiment/celery}
%\input{System/test_plan}
\input{System/proof_of_concept}

### 2016-05-14 rel_work.tex
fixed citation spaces

There are different approaches to finding vulnerabilities in web applications, two of them being Black-Box testing and White-Box testing.
Our work is based on the black-box testing approach to finding vulnerabilities on websites, and there has been plenty of research that has made use of this methodology \cite{Beizer:1995:BTT:202699}, \cite{Huang}, \cite{kals2006secubat}, \cite{payet13:ears-in-the-wild}, \cite{zanero2005automatic}. There has been significant discussion on both the benefits of such an approach \cite{black-box} and its shortcomings \cite{Doupe2012}, \cite{Doupe2010}.

Our work does not intend to act as a vulnerability scanner, but as a means to identify the presence of E-Mail Header Injection vulnerabilities in a given web application. In this sense, since we are injecting payloads into the web application, our work is related to other injection based attacks, such as SQL Injection \cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting --- XSS --- \cite{Injection1}, \cite{KleinAmit}, HTTP Header Injection \cite{sessionride}, and is very closely related to Simple Mail Transfer Protocol (SMTP) Injection \cite{Terada2015}.

The attack described by Terada \cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g. \texttt{To} e-mail header has a corresponding \texttt{To} SMTP header) to exploit the SMTP server's pipelining mechanism. The paper also describes proof-of-concept attacks against certain mailing libraries like \texttt{Ruby Mail} and \texttt{JavaMail}. This attack, although trying to achieve a similar result, is distinctly different from ours. The paper by itself makes this observation and discusses why it is different from E-Mail Header Injection.

@@

The first documented article dates to over a decade ago; a late 2004 article on phpsecure.info \cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the mail function in PHP, and how it can be exploited. Following this, we found other blog posts \cite{Calin}, \cite{DK}, \cite{Injection2}, \cite{Nicol}, \cite{Pope}, each describing how to exploit the vulnerability by using newlines to camouflage headers inside user input. A wiki entry \cite{Injection} also describes the ways to prevent such an attack. However, none of these articles have performed these attacks against real-life websites.

Another blog post written by user Voxel@Night on Vexatious Tendencies \cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes this vulnerability to be present. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plug-in to fix the discovered vulnerability.
\footnotetext{Note that this plugin is used actively on 300,000 websites (according to \cite{BestWebSoft2016}), but is yet to be fixed.}
The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}'' \cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section. \ref{Comp:Fuzzer:mp}).

>>>>

There are different approaches to finding vulnerabilities in web applications, two of them being Black-Box testing and White-Box testing.
Our work is based on the black-box testing approach to finding vulnerabilities on websites, and there has been plenty of research that has made use of this methodology~\cite{Beizer:1995:BTT:202699}, \cite{Huang}, \cite{kals2006secubat}, \cite{payet13:ears-in-the-wild}, \cite{zanero2005automatic}. There has been significant discussion on both the benefits of such an approach~\cite{black-box} and its shortcomings~\cite{Doupe2012}, \cite{Doupe2010}.

Our work does not intend to act as a vulnerability scanner, but as a means to identify the presence of E-Mail Header Injection vulnerabilities in a given web application. In this sense, since we are injecting payloads into the web application, our work is related to other injection based attacks, such as SQL Injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting --- XSS --- \cite{Injection1}, \cite{KleinAmit}, HTTP Header Injection~\cite{sessionride}, and is very closely related to Simple Mail Transfer Protocol (SMTP) Injection~\cite{Terada2015}.

The attack described by Terada~\cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g. \texttt{To} e-mail header has a corresponding \texttt{To} SMTP header) to exploit the SMTP server's pipelining mechanism. The paper also describes proof-of-concept attacks against certain mailing libraries like \texttt{Ruby Mail} and \texttt{JavaMail}. This attack, although trying to achieve a similar result, is distinctly different from ours. The paper by itself makes this observation and discusses why it is different from E-Mail Header Injection.

@@

The first documented article dates to over a decade ago; a late 2004 article on phpsecure.info~\cite{Tobozo} accredited to user \lstinline|tobozo@phpsecure.info| describing how this vulnerability existed in the reference implementation of the mail function in PHP, and how it can be exploited. Following this, we found other blog posts~\cite{Calin}, \cite{DK}, \cite{Injection2}, \cite{Nicol}, \cite{Pope}, each describing how to exploit the vulnerability by using newlines to camouflage headers inside user input. A wiki entry~\cite{Injection} also describes the ways to prevent such an attack. However, none of these articles have performed these attacks against real-life websites.

Another blog post written by user Voxel@Night on Vexatious Tendencies~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes this vulnerability to be present. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plug-in to fix the discovered vulnerability.
\footnotetext{Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.}
The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}'' \cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section. \ref{Comp:Fuzzer:mp}).
